Paper 2, Econ 980x

### 2022-12-09 Paper2.Rmd
commit

time_model <- newcsv1 %>%
  lm(formula = bls_leis ~ gender*year + age + race*new_educ)

@@

>>>>

time_model <- newcsv1 %>%
  mutate(year = as.character(year)) %>%
  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ )

@@

# W employment
time_model1 <- newcsv1 %>%
  mutate(year = as.character(year)) %>%
  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp)

summary(time_model1)
